---
title: "Assignment 02"
author: "Arshia Razavi"
date: "July 20, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
### R3 Markdown
#### R Markdown


#### 1.  Create two matrices from the given set of numbers X1 = {2,3,7,1,6,2,3,5,1} and x2={3,2,9,0,7,8,5,8,2}
```{r Q1}
X1 <- matrix (c(2,3,7,1,6,2,3,5,1), nrow = 3, ncol = 3)
X2 <- matrix (c(3,2,9,0,7,8,5,8,2), nrow = 3, ncol = 3) 

print(X1)
X2
```
#### 2. Find the matrix product.
```{r Q2}
matrixMultiplication <- X1*X2
matrixMultiplication


matrixMultiplication2 <- X1%*%X2
matrixMultiplication2
```
#### 3. Find the inverse of the matrix and prove that it is correct.
```{r Q3}
matrixInverseX1 <- X1 %*% solve(X1)
matrixInverseX1

solve(X1)

matrixInverseX2 <- X2 %*% solve(X2)
matrixInverseX2

matrixInverseX3 <- matrixMultiplication %*% solve(matrixMultiplication)
matrixInverseX3

matrixInverseX4 <- matrixMultiplication2 %*% solve(matrixMultiplication2)
matrixInverseX4
```
#### 4. Load Animals from MASS Package
```{r Q4}
library(MASS)
dataAnimals = Animals
dataAnimals
```
#### 5. Find the correlation coefficient of brain and body in this data set and comment on the relation between them
```{r Q5}
(animalsCorrelation <- cor(dataAnimals))

```
#### 6. load USArrest data set. Comment on the distribution of the Variables. Is there Any relation between UrbanPop and three crimes
```{r Q6}
library(MASS)
dataUSArrests <- USArrests
dataUSArrests
str(dataUSArrests)
summary(dataUSArrests)

dataUSArrestsCorrelation <- cor(dataUSArrests)
cor(dataUSArrests$UrbanPop, dataUSArrests$Murder)

```
The correlation coefficient is 0.069 . So we can conclude that the variables are positively linearly related. This means that if the states have more population the crime is related positively, hence the increase.

#### 7. Which states has most and least assault, murder, rape and arrests.
```{r Q7}
maxMurder <- dataUSArrests[which.max(dataUSArrests$Murder),]
maxMurder
maxAssault <- dataUSArrests[which.max(dataUSArrests$Assault),]
maxAssault
maxRape <- dataUSArrests[which.max(dataUSArrests$Rape),]
maxRape

minMurder <- dataUSArrests[which.min(dataUSArrests$Murder),]
minMurder
minAssault <- dataUSArrests[which.min(dataUSArrests$Assault),]
minAssault
minRape <- dataUSArrests[which.min(dataUSArrests$Rape),]
minRape
```
#### 8. List the states which have assault arrests more than median of the country
```{r Q8}
dataMeanMoreThanAssault <- dataUSArrests[dataUSArrests$Assault > (mean(dataUSArrests$Assault)),]
dataMeanMoreThanAssault
```
#### 9.  Which states are in the bottom 25% of the murder
```{r Q9}
totalMurder <- sum(USArrests$Murder)
summary(dataUSArrests)

more25percenTotalMurder <- dataUSArrests[which(dataUSArrests$Murder >= 11.250),]
more25percenTotalMurder
str(more25percenTotalMurder)
str(dataUSArrests)

```
#### 10. Which states are in the top 25% of the murder
```{r Q10}
less25percenTotalMurder <- dataUSArrests[which(dataUSArrests$Murder <= 4.075),]
less25percenTotalMurder
str(less25percenTotalMurder)
str(dataUSArrests)
```
